---
title: "README"
author: "DvP17"
date: "7/22/2019"
output:
  md_document:
    variant: markdown_github
---


<span style="color:red">**Methods on prevention of double-counting and constructing characterization factors were taken from:**</span>

Cabernard, L., Pfister, S., & Hellweg, S. (2019). A new method for analyzing sustainability performance of global supply chains and its application to material resources. Science of The Total Environment, 684, 164–177. https://doi.org/10.1016/j.scitotenv.2019.04.434


# Work with MRIO data

This R-package provides various methods for environmentally-extended multi-regional input–output (EE-MRIO) analysis. It offers different methods for calculating EEMRIO matrices and includes a set of diverse characterization factors.

* supports EXIOBASE3 and Eora
* characterization factors:
  + **b**iodiversity **l**oss `"bl"` (currently only for Exiobase)
  + **b**lue **w**ater consumption `"bw"` 
  + **c**limate **c**hange impacts `"cc"`
  + **en**ergy demand `"en"`
  + **l**and **u**se `"lu"`
  + **m**aterial **f**ootprint `"mf"`
  + **w**ater **s**tress `"ws"` (currently only for Exiobase)
* calculate:
  + **p**roduction to **d**emand matrix ``"pd"``
  + **p**roduction to target **d**emand matrix `"no-double-pt"`
  + **t**arget to final **s**upply matrix `"no-double-ts"`
  + **t**arget to final **d**emand matrix `"no-double-td"`
  + **p**roduction to final **d**emand matrix `"no-double-pd"`
* create country dyads


## First Steps

### 1 Install MRIO-Package
```{r eval=FALSE}
install.packages("remotes")
remotes::install_github("dvp17/mrio")
```

### 2 Calculate Matrix
Before you begin, set your working directory to the path where you store your Eora and Exiobase files:

e.g. `setwd("C:/Data/Exiobase")` or `setwd("C:/Data/Eora")`

```{r eval=FALSE}
setwd("C:/Data/Exiobase")
exio_cc <- mrio::exioloop(1995:2000, "cc", "pd")
utils::View(exio_cc[1:100,])
```
Please be aware that the process of calculating the matrices will take some time.

### 3 Create Dyads
```{r eval=FALSE}
setwd("C:/Data/Exiobase")
exio_cc_dyad <- mrio::dyads(1995:1996, exio_cc)
utils::View(exio_cc_dyad[1:100,])
```
Also the construction of the dyads is time-consuming. Please notice that no progress bar or estimated time for process completion is given before.

### 4 Look Into Characterization Factors
For further information on which extensions are included for which environmental impact, have a look on the characterization factors listed in the package. Notice that calculation of water stress and biodiversity loss is a little more complex, which makes it difficult to provide a simple list on those CFs.

```{r eval=FALSE}
utils::View(mrio::cf_eora)
utils::View(mrio::cf_eora[mrio::cf_eora$cf_cc > 0,])
```

## Recent Advancements

- added processing of pxp-matrices for EXIOBASE3

## Plan

- add WIOD data
- add `bl` and `ws` for Eora
- add `bl` for pxp-matrices
- include social indicators
- structural path calculation?
- implement function to download data automatically

